---
title: "Homework1"
author: "Meiju Chen"
date: "9/19/2020"
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high" ))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, factor_vec)) * pull(prob1_df, samp)
```



## Problem 2

After install the package, load the penguins dataset.

```{r}
data("penguins", package = "palmerpenguins")
```


Below is a short description of the penguins dataset.

1. The size of the dataset: `r nrow(penguins)`  rows and  `r ncol(penguins)` columns.
2. Three species: 'Adelie', 'Chinstrap', 'Gentoo'
3. Three locations: 'Biscoe', 'Dream', 'Torgersen'
4. The mean of bill length: `r mean(pull(penguins, bill_length_mm), na.rm = T)`
5. The mean of bill depth: `r mean(pull(penguins, bill_depth_mm), na.rm = T)`
6. The mean of flipper length: `r mean(pull(penguins, flipper_length_mm), na.rm = T)`


This is a scatterplot of flipper_length_mm (y) vs bill_length_mm (x).

```{r}
plot_df = 
  tibble(
    x = pull(penguins, bill_length_mm),
    y = pull(penguins, flipper_length_mm),
    species = pull(penguins, species)
  )

ggplot(plot_df, aes(x = x, y = y, color = species)) + geom_point()
ggsave("scatter_plot.pdf")
```



